\documentclass[
    type = bachelor,
    degree = academic,
    twoside,
    fontset = win,
    decl-page
]
{njuthesis}

\input{zhangjihua-thesis-setup.def}

\usepackage{listings} % 展示代码
\usepackage{algorithm,algorithmic} % 展示算法伪代码
\usepackage{subcaption} % 嵌套小幅图像，比 subfig 和 subfigure 更新更好
\usepackage{siunitx} % 标准单位符号

\newcommand{\TLA}{TLA\textsuperscript{+}\ }

\begin{document}
% 封面
\maketitle

\begin{abstract}
    分布式协议以及分布式系统，在当今的计算机世界不可或缺。自动化地对分布式协议验证其正确性是一个重要且困难的挑战。
    为了验证分布式协议的正确性，我们可以尝试证明分布式协议的每一个状态都满足一个预先给定的不变式，即安全属性(safety property)。
    对于复杂系统，我们无法像验证简单系统，通过遍历所有状态的方式来验证安全属性。
    过去的研究中往往采用寻找一个蕴含着安全属性的不变式的方式来验证协议的正确性，这个不变式经过所有可能的状态转移后仍然能保持其自身的正确性。
    这个不变式被称为归纳不变式。
    自动化地生成分布式协议的归纳不变式是验证自动化分布式协议正确性的关键步骤。

    以往的研究主要基于的IVy进行实现，\TLA 语言领域的相关研究较少。本文将提供一种基于\TLA 的归纳不变式生成工具，实现对以\TLA 语言描述的分布式协议规约的归纳不变式的自动化生成。
    与此同时，通过引入了强化学习的方法，加速归纳不变式的推导。
    引入外部工具 \href{https://apalache.informal.systems/}{apalache} 作为验证引擎，实现了对归纳不变式的验证。
    在进入强化学习模块之前，我们基于 tla2tools 对 \TLA 源文件进行静态分析，提取出语义信息，以便强化学习框架理解 \TLA 文件的语义。
    通过实验，本文提出的方法的有效性和可行性可以得到验证。
\end{abstract}
  
\begin{abstract*}
    Distributed Protocols and distributed systems are indispensable in today's computer world. Automatically verifying the correctness of distributed protocols is an important and challenging task.
    To verify the correctness of distributed protocols, we can try to prove that every state of the distributed protocol satisfies a pre-defined invariant, a safety property.
    For complex systems, we cannot verify safety properties by traversing all states as we do for simple systems.
    Researchers often use the method of finding an invariant that implies the safety property, which remains correct after all possible state transitions. This invariant is called an inductive invariant.
    Automatically generating inductive invariants for distributed protocols is a key step in verifying the correctness of automated distributed protocols.

    Previous research is mainly based on IVy for implementation, few on \TLA. 
    This paper will provide an inductive invariant generation tool based on \TLA, which realizes the automatic generation of inductive invariants for distributed protocol specifications described in \TLA language.
    Meanwhile, it accrelerates the derivation of inductive invariants by introducing reinforcement learning methods.
    The external tool \href{https://apalache.informal.systems/}{apalache} is introduced as a verification engine to verify the inductive invariants.
    Before entering the reinforcement learning module, we perform static analysis on the \TLA source files using tla2tools to extract semantic information for the reinforcement learning framework to understand the semantics of the \TLA files.
    Through experiments, the effectiveness and feasibility of the method proposed in this paper have been verified.
\end{abstract*}

% 目录
\tableofcontents

% 正文
\mainmatter
\include{chapters/introduction}

\include{chapters/pre-knowleage}

\include{chapters/conclusion}

% 生成参考文献页
\printbibliography

\begin{acknowledgement}
时光荏苒，四年的时间很快过去了。2020年9月3日大清早，拖着行李走进南大校门，穿过教学楼和一组团主干道的场景还历历在目，仿佛就在昨天，如今却快要到达四年本科学习的终点，走向下一段旅程。
本科四年，求学生涯，乃至人生到此的所有阶段，都离不开许多人的帮助和支持。

感谢父母，祖父母对我的养育之恩，对我生活和求学的支持。是他们的付出，让我有成长学习的环境。

感谢魏恒峰老师在学习生活上的指导。是他带领我进入科研的大门，让我了解分布式系统验证和形式化方法。

感谢诸位朋友的陪伴，开导，帮助和建议，人生因为你们而丰富多彩。

感谢党和国家对教育事业的支持。感谢南京大学，以及诸位老师，工作人员为我们提供了一个良好的学习环境。

\end{acknowledgement}

\end{document}